\documentclass[a4paper,10pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{filecontents}
\begin{filecontents}{abstract.bib}
@article{spes,
title = {Survey Paper on Elastic Search},
author = {Gupta, Pragya and Nair, Sreeja},
journal = {International Journal of Science and Research (IJSR)},
year = {2016},
month = {January}
},
@book{esdg,
title = {Elasticsearch: The Definitive Guide },
author = {Gormley,Clinton and Tong,Zachary },
publisher = {O'Reilly Media},
date = {January 2015}
},
@article{mmre,
title = {Mining Modern Repositories with Elasticsearch},
author = {Kononenko,Oleksii and Baysal,Olga and Holmes, Reid and Godfrey, Michael},
journal = {University of Waterloo, Waterloo, ON, Canada},
year = {2014}
},
@misc{site,
title = {Elasticsearch: Search and Analyze Data in Real Time},
author = {https://www.elastic.co/products/elasticsearch}
}

\end{filecontents}

\title{\Huge {\textbf {Elastic Search}}}
\author{
  \Large { Mohammed Nisham K } \\
  mnishamk1995@gmail.com \\
  \small Roll No 39, S7 CSE \\
  \\
  \Large {Guide : Vipin Vasu A V}\\
  vipin@cet.ac.in
}
\date{\today}

\begin{document}
\maketitle
\nocite{*}

\renewcommand{\abstractname}{\Large Abstract}
\begin{abstract}
Elastic search is a way to organize data and make it easily accessible. 
It is a server  based search on Lucene. It is a highly scalable, distributed and full-text search engine. 
Elastic search is developed in Java. It is published as open source under the terms of the Apache License. 
Elasticsearch is the most popular enterprise search engine. Elasticsearch includes all advances in speed, security, 
scalability, and hardware efficiency. Elastic search is a tool for querying written words. It can perform some other 
smart tasks, but its principal is returning text similar to a given query and statistical analyses of a quantity of text. 
Elasticsearch is a standalone database server,  which  is  written  in  Java and using HTTP/JSON protocol,it’s  takes  data  
and  optimizes  the  data  according  to  language  based searches and stores it in a sophisticated format. 
Elastic search is very convenient, supporting clustering and leader selection out of the box.  
Whether  it’s  searching  a  database  of  trade  products  by  description,  finding  similar  text  in  a  body  of  
crawled  web  pages. Elasticsearch is an excellent tool. 
\end{abstract}

\bibliography{abstract}{}
\bibliographystyle{plain}

\end{document}
